Formalizing Stack Safety as a Security Property

### 2023-01-17 submission5/core.tex
Finished reorg, largely

The stack governs a large number of language features that are often excluded
from discussion of stack safety. Our properties support a system with
both caller- and callee-saved registers, arguments passed on the stack,
exceptions, [tail call elimination, and concurrency.] They are modular by
design, in order to be further extensible to other features and architectures.

@@

Security mechanisms designed to prevent a certain class of attacks can be brittle---successfully
eliminating the attack as it exists at the time of publication, but leaving room for attackers
to find new, similar attacks. To mitigate this risk, mechanisms should aim to enforce formal
properties that can be proven or tested. Such properties become the specification against which
enforcement can be validated; even enforcement mechanisms that do not fulfill the property
benefit from the ability to articulate {\it why}.

Stack safety is challenging to specify in full generality, because the stack is fundamentally
an architecture-specific construct. (Contrast Acevedo de Amorim et al.'s \cite{} work on heap safety,
which is broadly consistent across architectures and therefore amenable to a very general approach.)
The desired behavior of the stack varies based on ISA, calling convention,
and the features of whichever programming language originated the code.
For instance, the current state-of-the-art stack-safety specification from Georges et al.
\cite{Georges22:TempsDesCerises} supposes a machine with only straightforward call-and-return
control flow, and therefore defines {\it Well-bracketed Control Flow} (WBCF) under the assumption that
a callee should always return to its caller. But, in the presence of tail-call elimination, a
return from a callee to a distant ancestor is perfectly reasonable. Subtle tweaks to the definition
accompany any addition to the model.

We are not attempting to create a universal definition of stack safety for all systems.
Rather, we define the stack safety of a single, fairly realistic system, decomposed into
(1) a lightweight model of the system and its security-relevant features, from which we
derive the integrity, confidentiality, and control-flow requirements of each call and
return, (2) the application of that model to a particular target system, and (3)
the formal criteria for integrity, confidentiality, and control flow
to obey the requirements.

We treat stack safety as multiple properties, rather than one multi-faceted property, because
not all enforcement mechanisms attempt to implement all of them. Some focus exclusively on
control flow, others protect the confidentiality of the caller but not the callee, etc.

@@

\section{Key Ideas}

@@

@@

The set of security-relevant operations (\(\Psi\)) covered in this paper is given in
the following table. Those that we explore in detail in Section \ref{sec:examples}
are shown in white: calls, returns, and the allocation and deallocation of local memory.
In the full formalism (Appendix \ref{app:full}) and the machine that we test,
we cover additional operations add parameters to our existing ones, to support
various forms of memory sharing and tail-call elimination. These are shown in light gray.
We give a proof-of-concept formalization of a more sophisticated, heap-like sharing model
based on pointer provenance in Appendix \ref{app:ptr}, represented by the dark grey
operations, but we do not test this.

@@

\begin{tabular}{| l | l |}
  \hline
  \(\psi \in \Psi\) & Parameters \\
  \hline
  \example \(\mathbf{call}\) & Target address \\
  \example & Argument registers \\
  \testing & Stack argument offset \& size \\
  \example \(\mathbf{return}\) & \\
  \example \(\mathbf{alloc}\) & Offset \& size \\
  \testing & Public flag \\
  \example \(\mathbf{dealloc}\) & Offset \& size \\
  \testing \(\mathbf{tailcall}\) & As \(\mathbf{call}\) \\
  \hline
  \multicolumn{2}{|c|}{{\it Pointer provenance operations}} \\
  \hline
  \theory \(\mathbf{promote}\) & Register, offset \& size \\
  \theory \(\mathbf{propagate}\) & Source register/address \\
  \theory & Destination register/address \\
  \theory \(\mathbf{clear}\) & Target register/address \\
  \hline
\end{tabular}

@@

\paragraph*{Variant States}

\paragraph*{Events and Traces}

It is common to specify the behavior of a system, including security properties, in
terms of traces of observable events rather than details of the machine state.
Lazy enforcement works because the deferred check catches errors before they appear
in the trace. The nature of traces varies based on the properties of interest, but
given a particular model of observation, we can consider
corruption by {\tt f} acceptable as long as it does not affect {\tt main}'s observable behavior.

@@

\section{Machine Model and Security Semantics}

\subsection{The Basic Machine}

The building blocks of the machine are {\em words} and {\em registers}.
Words are ranged over by \(\word\) and, when used as addresses, \(\addr\),
and are drawn from the set \(\WORDS\).
Registers in the set \(\REGS\) are ranged over by \(\reg\), with the stack pointer
given the special name \(\SP\);
some registers may be classified as caller-saved or callee-saved.
%
Along with the program counter, \(\PCname\), these are {\em state elements} \(\component\)
in the set \(\COMPONENTS ::= \PCname | \WORDS | \REGS\).

@@

A {\em machine state} \(\mach\) is a map from state elements to a set \(\mathcal{V}\) of
\emph{values}. Each value \(v\) contains a \emph{payload} word, written \(|v|\).
The details of value structure depend on the specific machine being modelled;
intuitively, the payload represents the part of the value that is relevant to
the behavior of the basic machine, while the rest of the value may contain
information relevant to a hardware enforcement mechanism (such as a tag).
We write \(\mach[\component]\) to denote the value of \(\mach\) at
\(\component\)  and \(\mach[v]\) as shorthand for \(\mach[|v|]\).

{\em Events} are drawn from a set \(\OBSS\)\bcp{lowercase?} and ranged over by \(\obs\), with a
special silent event \(\tau\).
The machine step function
\(\mach \xrightarrow{\overline{\psi},\obs} \mach' \in \MACHS \rightarrow
\MACHS \times \mathit{list} ~ \Psi \times \OBSS\)
is labeled by an ordered list of security-relevant operations, defined below,
and an event.

While some enforcement mechanisms may cause a machine to
failstop, we model this as the machine silently diverging by remaining in the
same state. We consider silently diverging traces to be indistinguishable
(from the point of view of an attacker) from traces that might eventually
produce output\bcp{why?}, an assumption that gives our properties the flavor of
{\it termination insensitivity}.

\subsection{Security-Relevant Operations, Principals, and State}

Security-relevant operations consist of calls, returns, and allocations.
Calls identify the address of the call's target,
plus the argument registers. Allocations and deallocations are phrased in terms of a pair
of an offset from the stack pointer and a size. Returns don't require any additional information.
%

%\[\context \in \CONTEXTS ::= \mathit{VIEW \times list ~ VIEW}\]
The initial context is \(\context_0 = (V_0, \emplist)\).

We have described informally how the security context develops as the system performs
security-relevant operations. Formally, we combine each machine state with a context
to create a {\it combined state} \(s = (\mach,\context)\) and a lift the transition
transition \(\stepstounder{}\) on combined states, labeled with the same operations.
with each step, the context updates based on the function
\(Op : \MACHS \rightarrow \CONTEXTS \rightarrow \psi \rightarrow \CONTEXTS\).
Note that \(Op\) takes as its first argument the state {\it before} the step.
Since a single step might correspond to multiple operations, we apply
\(Op\) as many times as is needed.

@@

The definition of \(Op\) is most convenient to present decomposed into
rules for each operation. In the simple system, the operations affect the
context as follows:

\judgmentbr[Alloc]
           {\(b = \mach[\SP] + \mathit{off}\)}
           {\(V' = V \llbracket \addr \mapsto \sealed |
             b \leq a < b+\mathit{sz} \land V ~ \addr = \unsealed \rrbracket\)}
           {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

@@

\section{Formalizing Properties}

\section{Advanced Machine}

The advanced machine defines additional operations, and extends some of the old ones.
It adds a field \(\overline{sa}\) to the \(\mathbf{call}\) operation, which is a set of
triples of a register, a base offset, and a size, and denotes that the object at the offset
from the given register is to be passed as an argument. The new \(\mathbf{tailcall}\) operation
has the same fields, but deals with tail call optimizations in which the callee will reuse
the caller's stack. The \(\mathbf{alloc}\) operation
gains a boolen flag indicating whether the allocation is to be public, accessible to
all functions until deallocated. And, we add the corresponding \(\mathbf{dealloc}\)
operation.

@@

Allocating public objects affects the call stack very similarly to private ones,
but instead of labeling them \(\object\) they become \(\public\), so they are
not sealed at a call. This makes these
regions of memory able to transmit information between caller and callee without
violating the stack safety properties. Note that there is no way to seal a location
once it has become \(\public\); only when {\tt x} is deallocated will its region
be available to allocate privately. We define a helper function, \(\mathit{range}\),
to map an offset from a register and a size into a set of addresses.
%
\[\mathit{range} ~ \reg ~ \mathit{off} ~ \mathit{sz} ~ \mach \triangleq
\{\mach[\reg]+i | \mathit{off} \leq i < \mathit{off+sz}\}\]
%
\judgmentbr[AllocPriv]
           {\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap
             \{\addr \mid V ~ \addr = \unsealed\}\)}
           {\(V' = V \llbracket \addr \mapsto \sealed \mid \addr \in \components \rrbracket\)}
           {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{f} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

\judgmentbr[AllocPub]
           {\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap
             \{\addr \mid V ~ \addr = \unsealed\}\)}
           {\(V' = V \llbracket \addr \mapsto \public \mid \addr \in \components \rrbracket\)}
           {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{t} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

\judgmentbr[Dealloc]
           {\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap
             \{\addr \mid V ~ \addr = \unsealed\}\)}
           {\(V' = V \llbracket \addr \mapsto \unsealed \mid \addr \in \components \rrbracket\)}
           {\(Op ~ \mach ~ (\mathbf{dealloc} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

@@

So we must refine our call operation to make use of the information that we have about
which memory contain arguments, \(\overline{sa}\). \(\overline{sa}\) is a set of
triples of a register, an offset from the value of that register, and a size.
We first define the helpful set \(\mathit{passed} ~ \overline{sa} ~ \mach\),
then extend the call operation to keep all objects in \(\mathit{passed}\) marked
as \(\object\) and seal everything else.
%
\[\mathit{passed} ~ \overline{sa} ~ \mach = \bigcup_{(\reg,\mathit{off},\mathit{sz}) \in \overline{sa}}
\mathit{range} ~ \reg ~ \mathit{off} ~ \mathit{sz} ~ \mach\]
%
\judgmentbrbr[]
             {\(\psi = \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa}\)}
             {\(V' = V \llbracket \reg \mapsto \unsealed | \reg \in \mathit{CLR} \rrbracket
               \llbracket \reg \mapsto \public | \reg \in \overline{\reg_{args}} \rrbracket\)}
             {\(V'' = V'\llbracket \addr \mapsto \sealed | V' ~ \addr = \object \land \addr \not \in (\mathit{passed} ~ \overline{sa} ~ \mach) \rrbracket\)}
             {\(Op ~ \mach ~ \psi ~ (V,\sigma) =
               (V'',V::\sigma)\)}

@@

\judgmentbrbr[]
             {\(\psi = \mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa}\)}
             {\(V' = V \llbracket \reg \mapsto \unsealed | \reg \in \mathit{CLR} \rrbracket
               \llbracket \reg \mapsto \public | \reg \in \overline{\reg_{args}} \rrbracket\)}
             {\(V'' = V'\llbracket \addr \mapsto \unsealed | V' ~ \addr = \object \land \addr \not \in (\mathit{passed} ~ \overline{sa} ~ \mach) \rrbracket\)}
             {\(Op ~ \mach ~ \psi ~ (V,\sigma) =
               (V',\sigma)\)}

@@

\subsection{Properties}
\label{sec:props}

>>>>

The stack governs a large number of language features that are often excluded
from discussion of stack safety. Our properties support a system with
both caller- and callee-saved registers, arguments passed on the stack,
tail-call elimination, [exceptions, and concurrency.] They are modular by
design, in order to be further extensible to other features and architectures.

@@

Security mechanisms designed to prevent a certain attack can be brittle---successfully
eliminating the attack as it exists at the time of publication, but leaving room for attackers
to find new, similar attacks. To mitigate this risk, mechanisms should aim to enforce formal
properties of correct behavior that can be proven or tested. Such properties become the
specification against which enforcement can be validated; even enforcement mechanisms that do
not fulfill the property benefit from the ability to articulate {\it why} they fail.

Stack safety is challenging to specify in full generality, because the stack is fundamentally
an architecture-specific construct. (Contrast Acevedo de Amorim et al.'s \cite{} work on heap safety,
which is broadly consistent across architectures and therefore amenable to a very general approach.)
The desired behavior of the stack varies based on ISA, calling convention,
and the features of whichever programming language originated the code.
For instance, the current state-of-the-art stack-safety specification from Georges et al.
\cite{Georges22:TempsDesCerises} supposes a machine with only straightforward call-and-return
control flow, and therefore defines {\it Well-bracketed Control Flow} (WBCF) under the assumption that
a callee should always return to its caller. But, in the presence of tail-call elimination, a
return from a callee to a distant ancestor is perfectly reasonable. Any addition of new features
must be accompanied by tweaks to the model.

We are not attempting to create a universal definition of stack safety for all systems.
Rather, we define the stack safety of a single, fairly realistic system, decomposed into
(1) a lightweight model of the system and its security-relevant features, from which we
derive the integrity, confidentiality, and control-flow requirements of each call and
return, (2) the application of that model to a particular target system, and (3)
the formal criteria for integrity, confidentiality, and control flow
to obey the requirements. We consider the criteria in (3) to represent universal definitions
that are parameterized by (1).

We treat stack safety as multiple properties, rather than one multi-faceted property, because
not all enforcement mechanisms attempt to implement all aspects of stack safety. Some focus
exclusively on control flow, others protect the confidentiality of the caller but not the
callee, etc.

@@

Our properties are termination insensitive: in order to support enforcement mechanisms
that failstop rather than execute dangerous code, the properties must treat failstops
as invisible to the attacker. We extend this insensitivity to all errors for simplicity.
This is consistent with our treatment of properties that specify the state after a return,
in that a callee that diverges for any reason will never reach the return, and will fulfill
the property vacuously.

\section{Key Ideas}
\label{sec:ideas}

@@

\paragraph*{Terminology and Notation}

The building blocks of a machine are {\em words} and {\em registers}.
Words are ranged over by \(\word\) and, when used as addresses, \(\addr\),
and are drawn from the set \(\WORDS\).
Registers in the set \(\REGS\) are ranged over by \(\reg\), with the stack pointer
given the special name \(\SP\);
some registers may be classified as caller-saved or callee-saved.
Along with the program counter, \(\PCname\), these are referred to as
{\em state elements} \(\component\) in the set \(\COMPONENTS ::= \PCname | \WORDS | \REGS\).

A {\em machine state} \(\mach \in \MACHS\) is a map from state elements to a set \(\mathcal{V}\) of
\emph{values}. Each value \(v\) contains a \emph{payload} word, written \(|v|\).
The details of value structure depend on the specific machine being modelled;
intuitively, the payload represents the part of the value that is relevant to
the behavior of the basic machine, while the rest of the value may contain
information relevant to a hardware enforcement mechanism (such as a tag).
We write \(\mach[\component]\) to denote the value of \(\mach\) at
\(\component\)  and \(\mach[v]\) as shorthand for \(\mach[|v|]\).

@@

The set of security-relevant operations (\(\Psi\)) covered in this paper is given in
\cref{tab:psi}. Those that we explore in detail in \cref{sec:examples}
are shown in white: calls, returns, and the allocation and deallocation of local memory.
In the full formalism (\cref{app:full}) and the machine that we test,
we cover additional operations add parameters to our existing ones, to support
various forms of memory sharing and tail-call elimination. These are shown in light gray.
We give a proof-of-concept formalization of a more sophisticated, heap-like sharing model
based on pointer provenance in \cref{app:ptr}, represented by the dark grey
operations, but we do not test this.

@@

\begin{table}
  \begin{tabular}{| l | l |}
    \hline
    \(\psi \in \Psi\) & Parameters \\
    \hline
    \example \(\mathbf{call}\) & Target address \\
    \example & Argument registers \\
    \testing & Stack argument offset \& size \\
    \example \(\mathbf{return}\) & \\
    \example \(\mathbf{alloc}\) & Offset \& size \\
    \testing & Public flag \\
    \example \(\mathbf{dealloc}\) & Offset \& size \\
    \testing \(\mathbf{tailcall}\) & As \(\mathbf{call}\) \\
    \hline
    \multicolumn{2}{|c|}{{\it Pointer provenance operations}} \\
    \hline
    \theory \(\mathbf{promote}\) & Register, offset \& size \\
    \theory \(\mathbf{propagate}\) & Source register/address \\
    \theory & Destination register/address \\
    \theory \(\mathbf{clear}\) & Target register/address \\
    \hline
  \end{tabular}
  \label{tab:psi}
\end{table}

@@

\paragraph*{Events, Steps, and Traces}

It is common to specify the behavior of a system, including security properties, in
terms of traces of observable {\em events} rather than details of the machine state.
Lazy enforcement works because the deferred check catches errors before they appear
in the trace. The nature of events is a parameter of the machine, and can be specialized
to any notion of observable behavior.

Events are ranged over by \(\obs\), and include the special silent event
\(\tau\). Traces are non-empty, potentially infinite (coinductive) series of
events, and traces are {\em similar} \(\obsT_1 \simeq \obsT_2\) if they are
equal up to deletion of \(\tau\) events. This means that an infinite silent trace is
similar to any trace, consistent with termination insensitivity.

A machine step function
\(\mach \xrightarrow{\overline{\psi},\obs} \mach' \in \MACHS \rightarrow
\MACHS \times \mathit{list} ~ \Psi \times \OBSS\)
is labeled by an ordered list of security-relevant operations and an event.
We lift it into the security semantics by adding a security context to the
state, giving us a combined step function
\(\mach,\context \stepstounder{\overline{\psi},\obs} \mach',\context' \in
\MACHS \times \CONTEXTS \rightarrow \MACHS \times \CONTEXT \times \mathit{list} ~ \Psi \times \OBSS\).
We will define \(\stepstounder{}\) informally in the next section, and formally
in \cref{sec:props}.

@@

\section{Machine and Security Semantics, Formally}
\label{sec:props}

@@

Recall from \cref{sec:ideas} that a machine is a map from state elements
to values, with a step function \(\mach \xrightarrow{\bar{\psi},\obs} \mach'\).
The step function is total---while some enforcement mechanisms may cause a machine
to failstop, we model this as the machine silently diverging by remaining in the
same state.

A view \(V\) maps elements to security classes, and a context consists of the
view of the active function together with a stack of inactive views.
The initial context is \(\context_0 = (V_0, \emplist)\).
%
\[\context \in \CONTEXTS ::= \mathit{VIEW \times list ~ VIEW}\]
%
We have described informally how the security context develops as the system performs
security-relevant operations. Formally, we combine each machine state with a context
to create a {\it combined state} \(s = (\mach,\context)\) and a lift the transition
transition \(\stepstounder{}\) on combined states, labeled with the same operations.
with each step, the context updates based on the function
\(Op : \MACHS \rightarrow \CONTEXTS \rightarrow \psi \rightarrow \CONTEXTS\).
Note that \(Op\) takes as its first argument the state {\it before} the step.
Since a single step might correspond to multiple operations, we apply
\(Op\) as many times as is needed.

@@

The definition of \(Op\) is most convenient to present decomposed into
rules for each operation. We have already seen the intuition behind the rules for
\(\mathbf{alloc}\), \(\mathbf{call}\), and \(\mathbf{ret}\). Their precise behavior
is found in \cref{fig:basicops}.

\begin{figure}
\judgmentbr[Alloc]
           {\(b = \mach[\SP] + \mathit{off}\)}
           {\(V' = V \llbracket \addr \mapsto \object |
             b \leq a < b+\mathit{sz} \land V ~ \addr = \unsealed \rrbracket\)}
           {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

\judgmentbr[Dealloc]
           {\(b = \mach[\SP] + \mathit{off}\)}
           {\(V' = V \llbracket \addr \mapsto \unsealed |
             b \leq a < b+\mathit{sz} \land V ~ \addr = \object \rrbracket\)}
           {\(Op ~ \mach ~ (\mathbf{dealloc} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

@@

         \caption{The basic operations}
         \label{fig:basicops}
\end{figure}

\subsection{Advanced Operations}

The advanced machine defines additional operations, and extends some of the old ones.
We add a field \(\overline{sa}\) to the \(\mathbf{call}\) operation: a set of
triples of a register \(\reg\), a base offset \(off\), and a size \(sz\), denoting
that the object at the offset \(off\) from \(\reg\) is to be passed as an argument.
The new \(\mathbf{tailcall}\) operation has the same fields, but deals with tail-call
optimizations in which the callee will reuse the caller's stack. The \(\mathbf{alloc}\) operation
gains a boolen flag indicating whether the allocation is to be public, accessible to
all functions until deallocated.

@@

Allocating public objects affects the call stack very similarly to private ones,
but instead of labeling them \(\object\) they become \(\public\), so they are
not sealed at a call. This makes these
regions of memory able to transmit information between caller and callee without
violating the stack safety properties. Note that there is no way to seal a location
once it has become \(\public\); only when {\tt x} is deallocated will its region
be available to allocate privately. We define a helper function, \(\mathit{range}\),
to map an offset from a register and a size into a set of addresses, and update
the operation's security semantics as shown in \cref{sfig:publicalloc}.

\begin{figure*}
  \begin{subfigure}{0.4\textwidth}
    \[\mathit{range} ~ \reg ~ \mathit{off} ~ \mathit{sz} ~ \mach \triangleq
    \{\mach[\reg]+i | \mathit{off} \leq i < \mathit{off+sz}\}\]

    \judgmentbr[]
               {\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap
                 \{\addr \mid V ~ \addr = \unsealed\}\)}
               {\(V' = V \llbracket \addr \mapsto \sealed \mid \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{f} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}

    \judgmentbr[]
               {\(\components = \mathit{range} ~ \SP ~ \mathit{off} ~ \mathit{sz} ~ \mach \cap
                 \{\addr \mid V ~ \addr = \unsealed\}\)}
               {\(V' = V \llbracket \addr \mapsto \public \mid \addr \in \components \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{alloc} ~ \mathbf{t} ~ \mathit{off, sz}) ~ (V,\sigma) = (V',\sigma)\)}
    \caption{Allocating Public Regions}
    \label{sfig:publicalloc}
  \end{subfigure}
  \begin{subfigure}{0.6\textwidth}
    %
    \[\mathit{passed} ~ \overline{sa} ~ \mach = \bigcup_{(\reg,\mathit{off},\mathit{sz}) \in \overline{sa}}
    \mathit{range} ~ \reg ~ \mathit{off} ~ \mathit{sz} ~ \mach\]
    %
    \judgmentbr[]
               {\(V' = V \llbracket \reg \mapsto \unsealed | \reg \in \mathit{CLR} \rrbracket
                 \llbracket \reg \mapsto \public | \reg \in \overline{\reg_{args}} \rrbracket\)}
               {\(V'' = V'\llbracket \addr \mapsto \sealed | V' ~ \addr = \object \land \addr \not \in (\mathit{passed} ~ \overline{sa} ~ \mach) \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{call} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa})
                 ~ (V,\sigma) = (V'',V::\sigma)\)}
    %
    \judgmentbr[]
               {\(V' = V \llbracket \reg \mapsto \unsealed | \reg \in \mathit{CLR} \rrbracket
                 \llbracket \reg \mapsto \public | \reg \in \overline{\reg_{args}} \rrbracket\)}
               {\(V'' = V'\llbracket \addr \mapsto \unsealed | V' ~ \addr = \object \land \addr \not \in (\mathit{passed} ~ \overline{sa} ~ \mach) \rrbracket\)}
               {\(Op ~ \mach ~ (\mathbf{tailcall} ~ \addr_{target} ~ \overline{\reg_{args}} ~ \overline{sa})
                 ~ (V,\sigma) = (V',\sigma)\)}
    \caption{Argument Passing on Stack}
    \label{sfig:stkargs}
  \end{subfigure}
  \caption{Advanced Operations}
  \label{fig:advops}
\end{figure*}

@@

So we must refine our call operation to make use of the information that we have about
which memory contain arguments, \(\overline{sa}\). \(\overline{sa}\) is a set of
triples of a register, an offset from the value of that register, and a size.
We first define the helpful set \(\mathit{passed} ~ \overline{sa} ~ \mach\),
then extend the call operation to keep all objects in \(\mathit{passed}\) marked
as \(\object\) and seal everything else (\cref{sfig:stkargs}).

@@

@@

\subsection{Properties}
\label{app:props}
